---
title: "Hw03-shrey-samdani"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, error = T, fig.path = 'images/')
```

## Piping

#### 2.1
```{bash}
cut -d "," -f 2 nba2017-roster.csv | tail +2 | sort -u > team-names.txt
head -5 team-names.txt
```

#### 2.2
```{bash}
cut -d "," -f 3 nba2017-roster.csv | tail +2 | sort -u > position-names.txt 
head -5 position-names.txt
```
#### 2.3
```{bash}
cut -d "," -f 7 nba2017-roster.csv | tail +2 | sort | uniq -c > experience-counts.txt
head -5 experience-counts.txt
```

#### 2.4
```{bash}
grep -e 'team' nba2017-roster.csv > LAC.csv
grep -e 'LAC' nba2017-roster.csv | sort >> LAC.csv
cat LAC.csv
```

#### 2.5
```{bash}
 grep -e 'LAL' nba2017-roster.csv | cut -d "," -f 6 | sort |  uniq -c
```

#### 2.6
```{bash}
grep -e 'CLE' nba2017-roster.csv | wc -l
```

#### 2.7
```{bash}
grep -e 'team' nba2017-roster.csv | cut -d "," -f 1,4,5 > gsw-height-weight.csv
grep -e 'GSW' nba2017-roster.csv | cut -d "," -f 1,4,5   >> gsw-height-weight.csv
cat gsw-height-weight.csv
```

#### 2.8
```{bash}
cut -d "," -f 1,8 nba2017-roster.csv | sort -t "," -k2 -r -n | head -10 > top10-salaries.csv
cat top10-salaries.csv
```

## Binomial Probability Functions
```{r}
source("code/binomial-functions.R")
```


* Assume that the “successful” event is getting a “six” when rolling a die. Consider
rolling a fair die 10 times. Use bin_probability() to find the probability of getting
exactly 3 sixes.
```{r}
bin_probability(10,3,1/6)
```


*  Use bin_distribution() to obtain the distribution of the number of “sixes” when
rolling a loaded die 10 times, in which the number “six” has probability of 0.25. Make
a plot of this distribution.
```{r}
distribution = bin_distribution(10,0.25)
plot(distribution)
```


* Use bin_probability(), and a for loop, to obtain the probability of getting more
than 3 heads in 5 tosses with a biased coin of 35% chance of heads.
```{r}
probability <- 0
for (i in 4:5) {
  probability = probability + bin_probability(5,i,0.35)
}
probability

```


* Use bin_distribution() to obtain the probability distribution of the number of heads
when tossing a loaded coin 15 times, with 35% chance of heads. Make a plot of this
distribution.
```{r}
distribution = bin_distribution(15,0.35)
plot(distribution)

```