---
title: "Getting started with dieroller"
author: "Shrey Samdani"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dieroller}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = T)
library(dieroller)
```



## Rolling a die
The package `"dieroller"` is an implementation for simulating rolling a die a given number of times, and to visualize the relative frequencies
in such a series of rolls.


## Creating a `die`

First, create a fair die as follows
```{r}
fair_die <- die()
fair_die
```

The probablities and outcome space can also be changed 
```{r}
# die with non-standard sides
weird_die <- die(sides = c('i', 'ii', 'iii', 'iv', 'v', 'vi'))
weird_die

# create a loaded die
loaded_die <- die(prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))
loaded_die
```


## Rolling a coin
Once you have defined a `"die"` object, you can use the function `roll()` to
_roll_ a coin a given number of `times`. The output will be an object of class 
`"roll"`, which will contain the vector of `rolls`:
```{r}
# roll 50 times
fair_50 <- roll(fair_die, times = 50)
fair_50
```

`summary()` can be used to observe the frequencies:
```{r}
summary(fair_50)
```

## Plot of relative frequencies

You can use the function `plot()` to create a graohic with the relative 
frequencies of a series of die rolls:
```{r, fig.show='hold'}
plot(fair_50)
```
