---
title: "Hw02-shrey-samdani"
output: github_document
author: "Shrey Samdani"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = '../images/')
```

```{r}
# import packages
library(dplyr)
library(ggplot2)
```

```{r}
# create charts
dat <- read.csv(file = '../data/shots-data.csv')

total_points <- 
dat %>%
  select(name) %>%
  group_by(name) %>%
  summarize(
    total = length(name)
  ) %>%
  arrange(desc(name))

esp <- 
  dat %>%
  select(name, shot_made_flag) %>%
  group_by(name) %>%
  summarize(
    total = length(name),
    made = length(shot_made_flag[shot_made_flag =='made shot']),
    perc_made = 100* made/total
  ) %>%
  arrange(desc(perc_made))

twopt <- 
  dat %>%
  select(name, shot_made_flag, shot_type) %>%
  group_by(name) %>%
  summarize(
    total = length(shot_type[shot_type == '2PT Field Goal']),
    made = length(shot_made_flag[shot_made_flag =='made shot' & shot_type == '2PT Field Goal']),
    perc_made = 100* made/total
  ) %>%
  arrange(desc(perc_made))

threept <- 
  dat %>%
  select(name, shot_made_flag, shot_type) %>%
  group_by(name) %>%
  summarize(
    total = length(shot_type[shot_type == '3PT Field Goal']),
    made = length(shot_made_flag[shot_made_flag =='made shot' & shot_type == '3PT Field Goal']),
    perc_made = 100* made/total
  ) %>%
  arrange(desc(perc_made))

esp
twopt
threept
```


```{r shooting_distance}
distances <- 
  dat %>%
  select(shot_distance, shot_made_flag) %>%
  group_by(shot_distance) %>%
  summarize(
    made_shot_prop = length(shot_made_flag[shot_made_flag == 'made shot']) / n()
  ) %>%
  arrange(shot_distance)

distances

ggplot(data = distances) + 
  geom_point(aes(x = shot_distance, y = made_shot_prop)) + 
  ggtitle('Shot Distance vs Percentage')

```

* What do you observe?  
As the distance increases, the shot percentage follows a downward trend.

* Can you confirm that the shorter the distance, the more effective the shots?
No; there are some data points that are higher in shot_distance but lower in made_shot_prop.

* Can you guesstimate a distance threshold beyond which the chance of making a successful shot is basically null?  
At/after around 34, most of the shots have a 0 proportion of success.

* What distances tend to have a percentage (of making a shot) of 50% or more?  
According to the graph, the distances 0,1,2,12,16,18,21,30,51 have a percentage of 50 or more.

```{r Total shots by minute of occurence}
data <- dat %>%
  select(name ,minute, period) %>%
  group_by(name,minute, period) %>%
  summarize(
    total_shots = n()
  ) %>%
  arrange(minute)

ggplot(data = data, aes(x = minute, y = total_shots, xmin = (period %% 2)*24, xmax = (period %% 2)*24 + 12, ymin = 0, ymax = 60)) + 
  scale_x_continuous(breaks = c(12,24,36,48)) + 
  geom_rect(fill = 'gray95') +
  geom_point(color = rgb(73,140,251,maxColorValue = 255)) +
  geom_path(color = rgb(73,140,251,maxColorValue = 255)) +
  theme_minimal() +
  labs(y= 'total number of shots',title ="Total number of shots (by minute of occurrence)") +
  facet_wrap(~ name)
  
```

